\documentclass[11pt]{article}
\usepackage{lmodern}

\input{head.tex}
\usepackage[backend=biber, style=ieee]{biblatex}
\usepackage{easylist}
\usepackage{hanging}
\usepackage{hyperref}
\usepackage{blindtext}
\usepackage{tipa}
\usepackage[left=2.5cm, top=2cm, bottom=2cm, right=2.5cm]{geometry}
\nocite{*}
\addbibresource{main.bib}

\title{Forecasting Rate of Spread of Covid19 using Linear Regression and LSTM}

\author{Ashwin Goyal*\\ \texttt{ashwingoyal180@gmail.com} \\
	 \and
	  Kartik Puri\\ \texttt{kartikpuri99@gmail.com}
	 \and
	Dr. Rachna Jain\\ \texttt{rachnajain.bvcoe@bvp.edu.in}
	 \and
	Dr. Preeti Nagrath\\ \texttt{preeti.nagrath@bharatividyapeeth.edu} \\
  }

\date{\small{Department of Electronics \& Communication Engineering} \\ \textbf{Bharati
Vidyapeeths College Of Enginnering}  \\ \today}

\begin{document}
\maketitle
\begin{abstract}
	COVID-19 virus, knows as novel coronavirus, spread across
	the world. The World Health Organisation (WHO), marked
	11\textsuperscript{th} March, 2020 as the day when COVID19 was
	declared as pandemic. It, was first
	originated in Wuhan, China.
	In recent days, Covid19 impacted various
	social and economic fields in the world.
	It is necesssary to
	quantify its spread and make predictions on how it is going to
	affect the world in coming months.
	In this paper, our aim is to use linear
	regression and LSTM algorithms to forecast of Covid19 spread.
	The objective of this study is to determine if spread can be
	forecasted to better accuracy using linear regression and LSTM
	algortihms.
	 \\

	KeyWords: Machine Learning, Linear Regression, LSTM, Mean
	Absolute Error, COVID-19
	\\
	\\
\end{abstract}

\pagenumbering{arabic}
\input{body.tex}

%\pagebreak
%\onecolumn
\printbibliography

\end{document}
